%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%  \cventry
%    {DevOps Engineer} % Job title
%    {Dunamu Inc.} % Organization
%    {Seoul, S.Korea} % Location
%    {Sep. 2023 - Present} % Date(s)
%    {
%    }

% %---------------------------------------------------------
%   \cventry
%     {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
%     {Danggeun Pay Inc. (KarrotPay)} % Organization
%     {Seoul, S.Korea} % Location
%     {Mar. 2021 - Jun. 2023} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Everything that matters.}
%         \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
%         \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
%         \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
%         \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
%         \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
%         \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {Site Reliability Engineer} % Job title
%     {Danggeun Market Inc.} % Organization
%     {Seoul, S.Korea} % Location
%     {Feb. 2021 - Mar. 2021} % Date(s)
%     {
%     }

%---------------------------------------------------------
  \cventry
    {Dev and Programming officer} % Job title
    {AUSTRALiAN BUREAU OF STATiSTiCS} % Organization
    {Canberra, Australia} % Location
    {Aug.2024 ‑ Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented robust GitLab CI/CD workflows to replace the to‑be‑deprecated Jenkins workflows, driving improvements in build
        automation and deployment efficiency. Wrote detailed documentation to facilitate a seamless transition for the team.}
        \item {Developed new features on main ETL system.}
        \item {Took responsibility for solving production issues as a member of the on‑call roster, ensuring system reliability.}
        \item {Refactored Java code to optimize the data acquisition workflow and improving its performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Backend Software Engineer } % Job title
    {MEGAPORT (AUSTRALiA) PTY LTD} % Organization
    {Brisbane(remote work), Australia} % Location
    {Apr.2022 ‑ Jun.2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a major project focused on developing a new microservice based authentication system. This lead to a higher security posture and
        set us up for a future, more flexible architecture.}
        \item {Was the primary maintainer for a microservice which centrally serviced a key client.}
        \item {Successfully developed and delivered a robust Multi‑Factor Authentication module, exceeding new feature requirements and significantly bol‑
        stering security protocols.}
        \item {Dramatically enhanced system performance by optimizing slow endpoints, leading to a marked improvement in user experience, streamlining
        QA processes, and accelerating GitLab pipeline workflows. I contributed to a 6‑7.5x improvement in pipeline timings, leading to increased
        delivery.}
        \item {Swiftly identified and rectified critical bugs, demonstrating exceptional problem‑solving skills to ensure customer satisfaction and maintain high
        service standards.}
        \item {Actively participated in group meetings, where I contributed to effective problem‑solving strategies and showcased significant project achieve‑
        ments.}
        \item {Managed the scheduling and execution of software releases, establishing a reliable and efficient release process that guaranteed seamless
        updates and system stability.}
        \item {Spearheaded the integration of asynchronous mode capabilities into the Megaport Cloud Router, marking a pivotal advancement in its func‑
        tionality and operational efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded System Engineer} % Job title
    {WiLDLiFE DRONES. CO., LTD. } % Organization
    {Canberra, Australia} % Location
    {Sep.2018 ‑ Jul.2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced the communication system between the payload and base, upgrading it to a bidirectional link, facilitating seamless and free‑flowing
        exchanges between the two.}
        \item {Optimized data transmission efficiency by selectively filtering payload data to include only relevant tag frequencies, significantly reducing critical
        data length.}
        \item {Successfully developed and integrated complete control logic for payload operations through the base, enabling comprehensive remote man‑
        agement.}
        \item {Achieved a substantial reduction in RTL‑SDR sampling duration through strategic code refactoring, thereby increasing the volume of tracking
        data collected during each field experiment}
        \item {Advanced the precision of target localization by devising and implementing more sophisticated signal processing algorithms, enhancing overall
        position accuracy.}
        \item {Introduced an innovative feature that allows users to calibrate the Raspberry Pi Sense HAT directly via our application, eliminating the need for
        complex terminal commands.}
        \item {Authored MATLAB scripts for meticulous analysis of experimental data, generating detailed reports for executive review, thereby informing
        strategic decisions at the CEO level.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
